---
title: "EDS 212 Day 5 Comp 1"
author: "Carly"
format: 
  html:
    code-fold: true
    code-summary: "Code Here:"
editor: visual
execute: 
  echo: true
  warning: false
---

**General Notes:**

\>\>Add "execute" in the YAML text above to suppress error messages or unnecessary code

\>\>Add additional html options under format in the YAML to fold the code with clicks and also show a summary to make the rendered window less cluttered

```{r}
library(tidyverse)
```

## Exploring Star Wars Dataset

-   Let's look at the first 6 lines (use head)

-   Find the dimensions of star wars (use dim)

-   Make a histogram of character heights (use ggplot and geom_histogram)

-   Make a scatter plot of height vs weight (use ggplot and geom_point)

```{r}
head(starwars)
dim(starwars)
#87 rows, 14 columns is how it's read

ggplot(data = starwars, aes(x = height)) + geom_histogram(fill = "maroon") + labs(x = "Height in cm", y = "Count")

```

```{r}
ggplot(data = starwars, aes(x = height, y = mass)) + geom_point(color = "blue")

```

## Calculate Summary Statistics

We are going to use mean() and sd() functions

If you have missing or NA values in a vector, the default is for the mean/sd functions to return an "NA". We can use "na.rm" and set it to TRUE to remove the NA values.

```{r}
mean_height <- mean(starwars$height, na.rm = TRUE)
mean_height
```

```{r}
sd_height <- sd(starwars$height, na.rm = TRUE)
sd_height
```
